### 2020-02-18 thesis/paper.tex
edit

Another aspect of consensus clustering that is only rarely touched on is how to select and generate base clusterings before applying consensus functions. The idea of this tool, to use meta-clustering for this step, is based on choosing robust clusterings but other aspects may be equally valuable to consider. An analysis on how different generation mechanisms impact the quality of the consensus result or the need for more base clusterings to find a similarly accurate result could be very helpful.

@@

\section{Reflection of Work}
In this thesis I presented a new tool for finding clustering solutions with the help of visual elements and consensus clustering. Previous visual frameworks such as Clustervision \cite{Kwon2018ClustervisionVS} rank multiple different clustering results according to quality metrics which might be biased towards specific cluster structures and only allow for choosing individual results, basically ignoring knowledge gained from additional runs. The newly created tool avoids these problems by finding robust solutions through meta-clustering and creating final solution candidates with consensus clustering. This way no structure bias should occur and knowledge of additional runs is included in the final result. In the Experiments chapter (Chapter \ref{cha:experiments}) of this thesis I showed how this leads to improved solution accuracy and still allows for analysis of different candidate solutions. Based on these findings, it could be a good idea to put further research into finding robust solutions and create consensus results according to indicators of clustering robustness.

>>>>

Another aspect of consensus clustering that is only rarely touched on is how to select and generate base clusterings before applying consensus functions. The idea of this tool, to use meta-clustering for this step, is based on choosing robust clusterings but other aspects may be equally valuable to consider. An analysis on how different generation mechanisms impact the quality of the consensus result or the need for more base clusterings to find a similarly accurate result could be very helpful. Besides filtering out some solutions and ignoring them in the consensus function, weighting them in relevance may also be interesting to look at.

@@

\section{Reflection of Work}
In this thesis I presented a new tool for finding clustering solutions with the help of visual elements and consensus clustering. Previous visual frameworks such as Clustervision \cite{Kwon2018ClustervisionVS} rank multiple different clustering results according to quality metrics which might be biased towards specific cluster structures and only allow for choosing individual results, basically ignoring knowledge gained from additional runs. The newly created tool avoids these problems by finding robust solutions through meta-clustering and creating final solution candidates with consensus clustering. This way no structure bias should occur and knowledge of additional runs is included in the final result. In the Experiments chapter (Chapter \ref{cha:experiments}) of this thesis I showed how this leads to improved solution accuracy and still allows generating different candidate solutions. Based on these findings, it could be a good idea to put further research into finding robust solutions and create consensus results according to indicators of clustering robustness. Generally, only little research has been put into the generation and selection of base clusterings for consensus, where accuracy improvements may be found.
